\bf A Hierarchical Model for Heterogenous Reliability Field Data

### 2018-04-22 paper/m-lb-m-technometrics.tex
fix the second typo

\section{Model Assessment}
\subsection{A simulation-based approach}
\label{model-assessment}
Having selected a model, it is good practice to check that the model provides an adequate representation of the data-generating mechanism. One way to do this is to draw replicate data sets from the posterior predictive distribution
$$p(t_{rep,g}|t) = \int f(t_{rep,g}|\theta_g)\; p(\theta_g|t)\;d\theta_g.$$
This is a general approach recommended by \cite{gelman1996postpred}, which works when no classical goodness-of-fit test is available. When the model is adequate for the data, the predictive distribution of a finite set of data characteristics --- chosen to reflect features relevant to the goals of the analysis --- should not contradict the corresponding characteristics observed in the actualized data.

@@

Because the variability in the K-M estimator is primarily a function of the number of at-risk units, we want to replicate the pattern of censoring that was observed. That is, for unit $i$ of sub-population $g$,
$$p(t_{rep,g}) = \int \prod_{i=1}^{n_g}f(t_{new}|t_{g,i}^L,c_{g,i},\theta)\,p(\theta|t)d\theta.$$
Because we are working with posterior draws, $\theta^{(s)}$, we can draw from this distribution by choosing a draw, $\theta^{(s)}$, at random, then conditionally draw $t_{rep,g}$ from $f(t_{new}|t_{g,i}^L,c_{g,i},\theta^{(s)}).$

>>>>

\section{Model Assessment}
\subsection{A simulation-based approach}
\label{model-assessment}
Having selected a model, it is good practice to check that the model provides an adequate representation of the data-generating mechanism. One way to do this is to draw replicate data sets from the posterior predictive distribution
$$p(t_{rep,g}|t) = \int \prod_{i=1}^{n_g} f(t|\theta_g)\; p(\theta_g|t)\;d\theta_g,$$
in the case that observations in subpopulation $g$ are exchangable.

This is a general approach recommended by \cite{gelman1996postpred}, which works when no classical goodness-of-fit test is available. When the model is adequate for the data, the predictive distribution of a finite set of data characteristics --- chosen to reflect features relevant to the goals of the analysis --- should not contradict the corresponding characteristics observed in the actualized data.

@@

Because the variability in the K-M estimator is primarily a function of the number of at-risk units, we want to replicate the pattern of censoring that was observed. To do this, we sample from a version of the posterior predictive that conditions on the observed truncation and censoring times, i.e. 
$$p(t_{rep,g}) = \int \prod_{i=1}^{n_g}f(t|t_{g,i}^L,c_{g,i},\theta)\,p(\theta|t)d\theta.$$
Because we are working with posterior draws, $\theta^{(s)}$, we can draw from this distribution by choosing a draw, $\theta^{(s)}$, at random, then conditionally draw each $t_{rep,g,i}$ from $f(t|t_{g,i}^L,c_{g,i},\theta^{(s)}).$
